PRIMUS: {\bf Effects of} Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-03-23 qfenv_paper/ApJ submission/qf_environment.tex
Edits of referee response

\begin{figure*}
    \begin{center}
        \leavevmode
	\includegraphics[scale=0.475]{fig1.pdf}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}. For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}

@@

{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments. Similar quiescent/red fraction studies (e.g. \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$. However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample. As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields. A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$. This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties. Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}

@@

{\bf We note that due to the redshift uncertainties in PRIMUS, our galaxy environment measures to more susceptible to contamination. Furthermore, as discussed in \cite{Coil:2011aa} and \cite{Cool:2013aa}, PRIMUS has a targeting fraction of $\sim 80 \%$ and redshift success rate of $> 75 \%$. zCOSMOS, in comparison, has $88 \%$ redshift completeness for the entire sample and $95 \%$ complete within the redshift range $0.5 < z < 0.8$ (\citealt{Lilly:2009aa}).}While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics. In addition, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$). Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.

@@

From our analyses we find the following notable results. The first
three demonstrate that previous findings that are well known in the
local universe are applicable out to $z\sim 0.7$. The last two are
consistent with the findings of \cite{Peng:2010aa} but provide increased
detail on the environmental dependence of galaxy evolution:
\begin{enumerate}
	\item From the SMFs, we find that the galaxy population in high
    density environments, both star-forming and quiescent, have a
    higher median mass, thus confirming the mass-density relation and
    mass-segregation in different environments throughout our sample's
    redshift range.
	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
    galaxy stellar mass, showing a clear mass dependence and
    reflecting the well-established color-mass and morphology-mass
    relations.
	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
    is greater than $f_{\mathrm{Q}}$ in low density environments
    for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$. This result
    reflects the well known trend that galaxies in high density
    environment are statistically redder, have lower SFRs, and are
    more massive.
	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
    low and high density environments. For high density environment,
    this trend is the Butcher-Oemler effect. Furthermore, the
    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
    existence of internal environment-independent mechanisms for
    ending star formation.
	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
    evolution for a range of environment classifications reveals that
    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
    in the highest density environments. For our purest high
    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
    evolution in low density environment, revealing a moderate
    dependence on environment.
\end{enumerate}

>>>>

\begin{figure*}
    \begin{center}
        \leavevmode
	\includegraphics[scale=0.475]{fig1.pdf}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to \cite{Coil:2011aa}. For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}

@@

{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments. Similar quiescent/red fraction studies (e.g. \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$. However we note for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample. As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the XMM-SXDS and XMM-CFHTLS PRIMUS fields are adjacent to one another. A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$. This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties. Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}

@@

{\bf Due to the redshift uncertainties in PRIMUS, our galaxy environment measures are more susceptible to contamination. Furthermore, as discussed in \cite{Coil:2011aa} and \cite{Cool:2013aa}, PRIMUS has a targeting fraction of $\sim 80 \%$ and redshift success rate of $> 75 \%$. zCOSMOS, in comparison, has $88 \%$ redshift completeness for the entire sample and $95 \%$ complete within the redshift range $0.5 < z < 0.8$ (\citealt{Lilly:2009aa}).}While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics. In addition, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$). Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.

@@

From our analyses we find the following notable results. The first
three demonstrate that previous findings that are well known in the
local universe are applicable out to $z\sim 0.7$. The last two are
consistent with the findings of \cite{Peng:2010aa} but provide increased
detail on the environmental dependence of galaxy evolution:
\begin{enumerate}
	\item From the SMFs, we find that the galaxy population in high
    density environments, both star-forming and quiescent, have a
    higher median mass, thus confirming the mass-density relation and
    mass-segregation in different environments throughout our sample's
    redshift range.
	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
    galaxy stellar mass, showing a clear mass dependence and
    reflecting the well-established color-mass and morphology-mass
    relations.
	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
    is greater than $f_{\mathrm{Q}}$ in low density environments
    {\bf for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$}. This result
    reflects the well known trend that galaxies in high density
    environment are statistically redder, have lower SFRs, and are
    more massive.
	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
    low and high density environments. For high density environment,
    this trend is the Butcher-Oemler effect. Furthermore, the
    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
    existence of internal environment-independent mechanisms for
    ending star formation.
	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
    evolution for a range of environment classifications reveals that
    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
    in the highest density environments. For our purest high
    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
    evolution in low density environment, revealing a moderate
    dependence on environment.
\end{enumerate}
